Eco-evolutionary dynamics of finite populations from first principles

### 2023-04-23 ind_files/02_math_background.tex
Make tracked changes in response to reviewer comments

Using this, and the fact that the future path of the Brownian motion itself is independent of its history, one can derive the following `multiplication table' for manipulating products of formal expressions of the form \eqref{ito_SDE_diff}:
\begin{center}
	\begin{tabularx}{0.4\textwidth}{ 
			| >{\centering\arraybackslash}X 
			| >{\centering\arraybackslash}X 
			| >{\centering\arraybackslash}X | }
		\hline
		& $\mathbf{dt}$ & $\mathbf{dW_t}$ \\
		\hline
		$\mathbf{dt}$ & $0$  &  $0$ \\ 
		\hline
		$\mathbf{dW_t}$ & $0$  & $dt$ \\
		\hline
	\end{tabularx}
\end{center}
One important but not immediately obvious consequence of this table is that we can no longer rely on the normal rules of calculus when dealing with stochastic integrals. In regular calculus, if we had a continuous quantity $x(t)$ satisfying

@@

I present a simple informal derivation in Appendix \ref{App_SDE_FPE} for the sake of completeness. Equation \eqref{ito_FPE} is called the `Fokker-Planck equation' in the physics and applied mathematics literature~\citep{gardiner_stochastic_2009} and is often called the `Kolmogorov forward equation' in the population genetics~\citep{ewens_mathematical_2004,barton_mathematical_2019} and pure mathematics~\citep{oksendal_stochastic_1998} literature. As I explain in Appendix \ref{App_SDE_FPE}, the Fokker-Planck equation can be viewed as a `conservation law' for probability that mathematically expresses the common-sense observation that the sum (or integral) of probabilities over the entire state space cannot change over time (since it must always equal 1). If the function $G$ is independent of $x$, it comes out of the derivatives in equation \eqref{ito_FPE}, and the resultant Fokker-Planck equation is said to be `linear' (and is much easier to solve).

This link between SDEs and Fokker-Planck equations goes both ways: One can show that every stochastic process with a probability density described by a Fokker-Planck equation of the form \eqref{ito_FPE} corresponds to the solution of an SDE of the form \eqref{ito_SDE_diff}, though the proof is much more technical and will not be discussed here. This two-way correspondence proves to be extremely useful, as one approach often works for applications in which the other fails. This correspondence makes it greatly desirable to be able to describe our stochastic process of interest as either the solution to an It\^o SDE of the form \eqref{ito_SDE_diff} or as the solution to a Fokker-Planck equation of the form \eqref{ito_FPE}. System-size expansions facilitate such a description for birth-death processes.

@@

\subsection{The intuition for the weak noise approximation in ecology}
If the parameter $K$ is sufficiently large, then the Fokker-Planck equation obtained via the system-size expansion can be further simplified to obtain a linear Fokker-Planck equation. This is accomplished by viewing the stochastic dynamics as fluctuating about a deterministic trajectory\footnote{This idea can be made much more rigorous via an analog of the central limit theorem for density-dependent Markov chains. See chapter 11, section 2 in~\citet{ethier_markov_1986}} (obtained by letting $K \to \infty$) and only works if $K$ is large enough to be able to neglect all but the highest-order terms. This is usually an excellent approximation for populations in which the deterministic trajectory has already reached an attractor (stable fixed point, stable limit cycle, etc.). Since many deterministic eco-evolutionary models are expected to relax to such attractors, such an approximation is a useful first step in increasing the generality of existing models (which are usually studied only in the equilibrium regime) to incorporate the dynamics of finite populations. Importantly, this approximation \emph{only} works if we can discard all but highest-order terms of $K$: Including higher-order terms leads to equations that do not form Fokker-Planck equations and do not even describe probability densities. As such, this approximation is best suited to describe populations that are `medium sized' - small enough that they cannot be assumed to be infinitely large, yet large enough that stochasticity is rather weak and the deterministic limit is somewhat predictive - a situation that occurs frequently in ecology and evolution.

@@

Consider a population of identical individuals subject to some ecological rules that affect individuals' birth and death rates. I will neglect any potential factor that could lead to two individuals becoming non-identical, like mutations, etc. Since all individuals are identical, we only really need to track the total population size through time to know everything there is to know about the population. The population as a whole at any time $t$ can thus be characterized by a single number - its population size (Figure \ref{fig_1D_pop_description}). Imagine further that if a population has $n$ identical individuals, then, from the ecological rules, we can determine a \emph{birth rate} $b(n)$, which gives us a measure of the probability that a new individual will be born and the population size becomes $n+1$ `per unit time'. One must be slightly precise about what exactly they mean when they say `per unit time' since there are no discrete `time steps' for individuals to be born. Here, by `birth rate', I mean the probability that there will be a birth (and no death) per an \emph{infinitesimal} amount of time. More formally, letting $N_t$ denote the random variable representing the population size at time $t$ and letting $\mathbb{P}(E)$ denote the probability (in the common-sense usage) of an event $E$, the birth rate\footnote{Note that unlike usual ecology convention, this is \emph{not} a per-capita birth rate. The ecology per capita birth and death rates can be found by dividing my birth/death rates by the current population size $n(t)$} $b(n)$ of individuals a population with population size $n$ is the quantity
\begin{equation}
\label{1D_birthrate_defn}
b(n) \coloneqq \lim_{\epsilon \to 0}\frac{1}{\epsilon}\mathbb{P}\left(N_{t+\epsilon}=n+1 | N_{t}=n\right)
\end{equation}
Exactly analogously, we can also define the \emph{death rate} $d(n)$ of individuals in a population of $n$ individuals as the quantity
\begin{equation}
\label{1D_deathrate_defn}
d(n) \coloneqq \lim_{\epsilon \to 0}\frac{1}{\epsilon}\mathbb{P}\left(N_{t+\epsilon}=n-1 | N_{t}=n\right)
\end{equation}
An alternative, perhaps more intuitive characterization, of these same quantities is the following: If we have a population of size $n$, and we know that \emph{either a birth or a death} is about to occur, then, the probability that the event that occurs is a birth is
\begin{equation*}
\mathbb{P\big[\textrm{ birth } \big{|} \textrm{ something happened }\big]} = \frac{b(n)}{b(n)+d(n)}
\end{equation*}
and the probability that the event is instead a death is
\begin{equation*}
\mathbb{P\big[\textrm{ death } \big{|} \textrm{ something happened }\big]} = \frac{d(n)}{b(n)+d(n)}
\end{equation*}
\begin{example}\label{ex_1D_stoch_logistic}
	Consider the case where the per-capita birth rate is a constant $\lambda > 0$, \emph{i.e}, $b(n) = \lambda n$, and the per-capita death rate has the linear density-dependence $\left(\mu + (\lambda-\mu)\frac{n}{K}\right)$, \emph{i.e.} the total death rate is $d(n) = \left(\mu + (\lambda-\mu)\frac{n}{K}\right)n$, where $\mu$ and $K$ are positive constants. Taking the difference between the birth and death rates, we obtain $b(n) - d(n) = (\lambda - \mu)n\left(1-\frac{n}{K}\right)$, where, identifying $r=\lambda-\mu$, we obtain the familiar logistic equation on the RHS. Note, however, that the population itself is stochastic, whereas the logistic equation is a deterministic description.
\end{example}
Now, let $P(n,t)$ be the probability that the population size is $n$ at time $t$. We wish to have an equation to describe how $P(n,t)$ changes with time - this will provide a probabilistic description of how we expect the population size to change over time.

@@

We observe that for any fixed $r$, the coefficient of $K^{-r/2}$ on the LHS is $\frac{\partial \Tilde{P}_r}{\partial s}$. On the RHS, the coefficients of $K^{-r/2}$ in the second term have the form $\Tilde{P}_{m}A^+_{n}y^n$, subject to the constraint that $m+n=r$. Furthermore, all such terms (and only such terms) are coefficients of $K^{-r/2}$. Thus, after grouping, the coefficient of $K^{-r/2}$ from the second terms of the RHS of \eqref{weak_noise_full_series_expansion} is precisely
\begin{equation*}
\frac{1}{2}\frac{\partial^2}{\partial y^2}\sum\limits_{m=0}^{r}\Tilde{P}_{m}A^+_{r-m}y^{r-m}
\end{equation*}
Exactly analogous reasoning reveals that the contribution of the first term of the RHS is:
\begin{equation*}
-\frac{\partial}{\partial y}\sum\limits_{m=0}^{r}\Tilde{P}_{m}A^-_{r-m+1}y^{r-m+1}
\end{equation*}
Thus, we find that the $r$th term of the expansion satisfies:
\begin{equation}
\label{weak_noise_expansion_each_term}
\frac{\partial \Tilde{P}_r}{\partial s} = -\frac{\partial}{\partial y}\left(\sum\limits_{m=0}^{r}\Tilde{P}_{m}A^-_{r-m+1}y^{r-m+1}\right) + \frac{1}{2}\frac{\partial^2}{\partial y^2}\left(\sum\limits_{m=0}^{r}\Tilde{P}_{m}A^+_{r-m}y^{r-m}\right)
\end{equation}
We will now make the meaning of `weak' precise. Let us assume that the fluctuations are weak enough that we can obtain a reasonable approximation of the dynamics by retaining only the highest order (in $1/K$) term in equation \eqref{weak_noise_expansion_each_term} and neglecting all higher-order terms\footnote{For example, we may imagine this is reasonable if the deterministic trajectory is at a stable fixed point and subject to weak fluctuations}. We are then left with the expression:
\begin{equation}
\label{1D_WNA}
\frac{\partial \Tilde{P}_0}{\partial s} = -A^-_1(s)\frac{\partial}{\partial y}(y\Tilde{P}_0) + \frac{A^+_{0}(s)}{2}\frac{\partial^2 \Tilde{P}_{0}}{\partial y^2}
\end{equation}
which is simply the Fokker-Planck equation for the It\^{o} process
\begin{equation*}
dY_t = A^-_1(t)Y_tdt + \sqrt{A^+_0(t)}dW_t
\end{equation*}
This is the `weak noise approximation', (sometimes also called the `linear noise approximation' because the resulting Fokker-Planck equation is linear). This equation describes a so-called `Ornstein-Uhlenbeck process', and is easily solved by using $\exp(-\int A^-_1(s)ds)$ as an `integrating factor'. In particular, multiplying both sides by $\exp(-\int A^-_1(s)ds)$ yields
\begin{align*}
\exp\left(-{\int\limits_{0}^{t}A^-_1(s)ds}\right)dY_t - Y_tA^-_1(t)\exp\left(-{\int\limits_{0}^{t}A^-_1(s)ds}\right)dt &= \sqrt{A^+_0(t)}\exp\left(-{\int\limits_{0}^{t}A^-_1(s)ds}\right)dW_t\\
\Rightarrow d\left(\exp\left(-{\int\limits_{0}^{t}A^-_1(s)ds}\right)Y_t\right) &= \sqrt{A^+_0(t)}\exp\left(-{\int\limits_{0}^{t}A^-_1(s)ds}\right)dW_t
\end{align*}
Integrating both sides and noting that $A^+_0(s) = A^+(\alpha(s))$, we thus obtain the final expression
\begin{equation}
\label{weak_noise_OU_solution}
Y_t = Y_0\exp\left({\int\limits_{0}^{t}A^-_1(s)ds}\right)+\int\limits_{0}^{t}\exp\left(-\int\limits_{s}^{t}A^-_{1}(v)dv\right)\sqrt{A^+(\alpha(s))}dW_s
\end{equation}
as the zeroth-order weak noise approximation for stochastic fluctuations from the deterministic trajectory due to demographic noise Note that this is an exact equation, and one can get many insights from it. For example, if $Y_0 = 0$ (\emph{i.e} we start at the deterministic steady state, a natural assumption for measuring fluctuations from it), then we can show by taking expectations in \eqref{weak_noise_OU_solution} and using results presented in \ref{intro_SDE} that we must have $\mathbb{E}[Y_t | Y_0] = 0$. In other words, the fluctuations have zero expectation and are expected to occur symmetrically about $\alpha(t)$), with no bias. The variance (spread) of the fluctuations $Y_t$, as well as higher moments, can also be exactly calculated from \eqref{weak_noise_OU_solution} using some tools from stochastic calculus, but I will not demonstrate this here.

Importantly, higher order terms do not form Fokker-Planck equations, and in general, $\Tilde{P}_r$ for $r>0$ may be negative and therefore does not even describe a probability. As such, formulating the solution as the solution to an SDE only works for $\Tilde{P}_0$. If noise is large enough that it is not well-approximated by $\Tilde{P}_0$, this method is not very useful.

>>>>

\textcolor{red}{\st{Using this, and the fact that the future path of the Brownian motion itself is independent of its history, one can derive the following `multiplication table' for manipulating products of formal expressions containing stochastic integrals with respect to the Brownian motion}} One important but not immediately obvious consequence of \textcolor{red}{\st{this table}} \textcolor{blue}{the definition of stochastic integrals and the Brownian motion} is that we can no longer rely on the normal rules of calculus when dealing with stochastic integrals. In regular calculus, if we had a continuous quantity $x(t)$ satisfying

@@

I present a simple informal derivation in Appendix \ref{App_SDE_FPE} for the sake of completeness. Equation \eqref{ito_FPE} is called the `Fokker-Planck equation' in the physics and applied mathematics literature~\citep{gardiner_stochastic_2009} and is often called the `Kolmogorov forward equation' in the population genetics~\citep{ewens_mathematical_2004,barton_mathematical_2019} and pure mathematics~\citep{oksendal_stochastic_1998} literature. As I explain in Appendix \ref{App_SDE_FPE}, the Fokker-Planck equation can be viewed as a `conservation law' for probability that mathematically expresses the common-sense observation that the sum (or integral) of probabilities over the entire state space cannot change over time (since it must always equal 1). If the function $G$ is independent of $x$, it comes out of the derivatives in equation \eqref{ito_FPE}, and the resultant Fokker-Planck equation is said to be `linear' (and is much easier to solve). \textcolor{blue}{It bears noting that the Fokker-Planck equation is always linear in the probability density $P(x,t)$, and thus the linearity here means that the equation is linear in the \emph{noise} term in the corresponding SDE~\citep{van_kampen_stochastic_1981,gardiner_stochastic_2009}.}

This link between SDEs and Fokker-Planck equations goes both ways: One can show that every stochastic process with a probability density described by a Fokker-Planck equation of the form \eqref{ito_FPE} corresponds to the solution of an SDE of the form \eqref{ito_SDE_diff}, though the proof is much more technical and will not be discussed here. This two-way correspondence proves to be extremely useful, \textcolor{red}{\st{as one approach often works for applications in which the other fails.}} \textcolor{blue}{since the two formulations are complementary and one may be much easier than the other for solving a particular problem}. This correspondence makes it greatly desirable to be able to describe our stochastic process of interest as either the solution to an It\^o SDE of the form \eqref{ito_SDE_diff} or as the solution to a Fokker-Planck equation of the form \eqref{ito_FPE}. System-size expansions facilitate such a description for birth-death processes.

@@

\subsection{The intuition for the weak noise approximation in ecology}
If the parameter $K$ is sufficiently large, then the Fokker-Planck equation obtained via the system-size expansion can be further simplified to obtain a linear Fokker-Planck equation. This is accomplished by viewing the stochastic dynamics as fluctuating about a deterministic trajectory\footnote{This idea can be made much more rigorous via an analog of the central limit theorem for density-dependent Markov chains. See chapter 11, section 2 in~\citet{ethier_markov_1986}} (obtained by letting $K \to \infty$) and only works if $K$ is large enough to be able to neglect all but the highest-order terms. This is usually an excellent approximation for populations in which the deterministic trajectory has already reached an attractor (stable fixed point, stable limit cycle, etc.). Since many deterministic eco-evolutionary models are expected to relax to such attractors, such an approximation is a useful first step in increasing the generality of existing models (which are usually studied only in the equilibrium regime) to incorporate the dynamics of finite populations.\textcolor{red}{\st{Importantly, this approximation \emph{only} works if we can discard all but highest-order terms of $K$: Including higher-order terms leads to equations that do not form Fokker-Planck equations and do not even describe probability densities. As such,}} This approximation is best suited to describe populations that are `medium sized' - small enough that they cannot be assumed to be infinitely large, yet large enough that stochasticity is rather weak and the deterministic limit is somewhat predictive - a situation that occurs frequently in ecology and evolution.

@@

Consider a population of identical individuals subject to some ecological rules that affect individuals' birth and death rates. I will neglect any potential factor that could lead to two individuals becoming non-identical \textcolor{blue}{in their birth and death rates}, like mutations, etc. Since all individuals are identical \textcolor{blue}{in their birth and death rates}, we only really need to track the total population size through time to know everything there is to know about the population. The population as a whole at any time $t$ can thus be characterized by a single number - its population size (Figure \ref{fig_1D_pop_description}). Imagine further that if a population has $n$ identical individuals, then, from the ecological rules, we can determine a \emph{birth rate} $b(n)$, which gives us a measure of the probability that a new individual will be born and the population size becomes $n+1$ `per unit time'. One must be slightly precise about what exactly they mean when they say `per unit time' since there are no discrete `time steps' for individuals to be born. Here, by `birth rate', I mean the probability that there will be a birth (and no death) per an \emph{infinitesimal} amount of time. More formally, letting $N_t$ denote the random variable representing the population size at time $t$ and letting $\mathbb{P}(E)$ denote the probability (in the common-sense usage) of an event $E$, the birth rate\footnote{Note that unlike usual ecology convention, this is \emph{not} a per-capita birth rate. The ecology per capita birth and death rates can be found by dividing my birth/death rates by the current population size $n(t)$} $b(n)$ of individuals a population with population size $n$ is the quantity
\begin{equation}
\label{1D_birthrate_defn}
b(n) \coloneqq \lim_{\epsilon \to 0}\frac{1}{\epsilon}\mathbb{P}\left(N_{t+\epsilon}=n+1 | N_{t}=n\right)
\end{equation}
Exactly analogously, we can also define the \emph{death rate} $d(n)$ of individuals in a population of $n$ individuals as the quantity
\begin{equation}
\label{1D_deathrate_defn}
d(n) \coloneqq \lim_{\epsilon \to 0}\frac{1}{\epsilon}\mathbb{P}\left(N_{t+\epsilon}=n-1 | N_{t}=n\right)
\end{equation}
An alternative, perhaps more intuitive characterization, of these same quantities is the following: If we have a population of size $n$, and we know that \emph{either a birth or a death} is about to occur, then, the probability that the event that occurs is a birth is
\begin{equation*}
\mathbb{P\big[\textrm{ birth } \big{|} \textrm{ something happened }\big]} = \frac{b(n)}{b(n)+d(n)}
\end{equation*}
and the probability that the event is instead a death is
\begin{equation*}
\mathbb{P\big[\textrm{ death } \big{|} \textrm{ something happened }\big]} = \frac{d(n)}{b(n)+d(n)}
\end{equation*}
\begin{example}\label{ex_1D_stoch_logistic}
	Consider the case where the per-capita birth rate is a constant $\lambda > 0$, \emph{i.e}, $b(n) = \lambda n$, and the per-capita death rate has the linear density-dependence $\left(\mu + (\lambda-\mu)\frac{n}{K}\right)$, \emph{i.e.} the total death rate is $d(n) = \left(\mu + (\lambda-\mu)\frac{n}{K}\right)n$, where $\mu$ and $K$ are positive constants. Taking the difference between the birth and death rates, we obtain $b(n) - d(n) = (\lambda - \mu)n\left(1-\frac{n}{K}\right)$, where, identifying $r=\lambda-\mu$, we obtain the familiar \textcolor{blue}{functional form of the density dependence of the} logistic equation \textcolor{red}{\st{on the RHS}}. Note, however, that the population itself is stochastic, whereas the logistic equation is a deterministic description.
\end{example}
Now, let $P(n,t)$ be the probability that the population size is $n$ at time $t$. We wish to have an equation to describe how $P(n,t)$ changes with time - this will provide a probabilistic description of how we expect the population size to change over time.

@@

We observe that for any fixed $r$, the coefficient of $K^{-r/2}$ on the LHS is $\frac{\partial \Tilde{P}_r}{\partial s}$. On the RHS, the coefficients of $K^{-r/2}$ in the second term have the form $\Tilde{P}_{m}A^+_{n}y^n$, subject to the constraint that $m+n=r$. Furthermore, all such terms (and only such terms) are coefficients of $K^{-r/2}$. Thus, after grouping, the coefficient of $K^{-r/2}$ from the second terms of the RHS of \eqref{weak_noise_full_series_expansion} is precisely
\frac{1}{2}\frac{\partial^2}{\partial y^2}\sum\limits_{m=0}^{r}\Tilde{P}_{m}A^+_{r-m}y^{r-m}
Exactly analogous reasoning reveals that the contribution of the first term of the RHS is:
-\frac{\partial}{\partial y}\sum\limits_{m=0}^{r}\Tilde{P}_{m}A^-_{r-m+1}y^{r-m+1}
Thus, we find that the $r$th term of the expansion satisfies:
\label{weak_noise_expansion_each_term}
\frac{\partial \Tilde{P}_r}{\partial s} = -\frac{\partial}{\partial y}\left(\sum\limits_{m=0}^{r}\Tilde{P}_{m}A^-_{r-m+1}y^{r-m+1}\right) + \frac{1}{2}\frac{\partial^2}{\partial y^2}\left(\sum\limits_{m=0}^{r}\Tilde{P}_{m}A^+_{r-m}y^{r-m}\right)
We will now make the meaning of `weak' precise. Let us assume that the fluctuations are weak enough that we can obtain a reasonable approximation of the dynamics by retaining only the highest order (in $1/K$) term in equation \eqref{weak_noise_expansion_each_term} and neglecting all higher-order terms\footnote{For example, we may imagine this is reasonable if the deterministic trajectory is at a stable fixed point and subject to weak fluctuations}. We are then left with the expression:
\label{1D_WNA}
\frac{\partial \Tilde{P}_0}{\partial s} = -A^-_1(s)\frac{\partial}{\partial y}(y\Tilde{P}_0) + \frac{A^+_{0}(s)}{2}\frac{\partial^2 \Tilde{P}_{0}}{\partial y^2}
which is simply the Fokker-Planck equation for the It\^{o} process
dY_t = A^-_1(t)Y_tdt + \sqrt{A^+_0(t)}dW_t
This is the `weak noise approximation', (sometimes also called the `linear noise approximation' because the resulting Fokker-Planck equation is linear). This equation describes a so-called `Ornstein-Uhlenbeck process', and is easily solved by using $\exp(-\int A^-_1(s)ds)$ as an `integrating factor'. In particular, multiplying both sides by $\exp(-\int A^-_1(s)ds)$ yields
\exp\left(-{\int\limits_{0}^{t}A^-_1(s)ds}\right)dY_t - Y_tA^-_1(t)\exp\left(-{\int\limits_{0}^{t}A^-_1(s)ds}\right)dt &= \sqrt{A^+_0(t)}\exp\left(-{\int\limits_{0}^{t}A^-_1(s)ds}\right)dW_t\\
\Rightarrow d\left(\exp\left(-{\int\limits_{0}^{t}A^-_1(s)ds}\right)Y_t\right) &= \sqrt{A^+_0(t)}\exp\left(-{\int\limits_{0}^{t}A^-_1(s)ds}\right)dW_t
Integrating both sides and noting that $A^+_0(s) = A^+(\alpha(s))$, we thus obtain the final expression
\label{weak_noise_OU_solution}
Y_t = Y_0\exp\left({\int\limits_{0}^{t}A^-_1(s)ds}\right)+\int\limits_{0}^{t}\exp\left(-\int\limits_{s}^{t}A^-_{1}(v)dv\right)\sqrt{A^+(\alpha(s))}dW_s
as the zeroth-order weak noise approximation for stochastic fluctuations from the deterministic trajectory due to demographic noise. \textcolor{red}{\st{Note that this is an exact equation}} 
\textcolor{blue}{This equation can be exactly solved via analytical techniques} and one can get many insights from the solution. For example, if $Y_0 = 0$ (\emph{i.e} we start at the deterministic steady state, a natural assumption for measuring fluctuations from it), then we can show by taking expectations in \eqref{weak_noise_OU_solution} and using results presented in \ref{intro_SDE} that we must have $\mathbb{E}[Y_t | Y_0] = 0$. In other words, the fluctuations have zero expectation and are expected to occur symmetrically about $\alpha(t)$), with no bias. The variance (spread) of the fluctuations $Y_t$, as well as higher moments, can also be exactly calculated from \eqref{weak_noise_OU_solution} using some tools from stochastic calculus, but I will not demonstrate this here.

Importantly, higher order terms do not form Fokker-Planck equations, and in general, $\Tilde{P}_r$ for $r>0$ may be negative and therefore does not even describe a probability. As such, formulating the solution as the solution to an SDE only works for $\Tilde{P}_0$. If noise is large enough that it is not well-approximated by $\Tilde{P}_0$, this \textcolor{blue}{approximation} \textcolor{red}{\st{method}} is not very useful.
